Davos: a Python package ``smuggler'' for constructing lightweight reproducible notebooks

### 2023-07-12 paper/main.tex
fix for frontmatter bug, edits to abstract

\title{Davos: a Python package ``smuggler'' for constructing
  lightweight reproducible notebooks}
\author{Paxton C. Fitzpatrick}
\author{Jeremy R. Manning\corref{cor}}
\ead{Jeremy.R.Manning@Dartmouth.edu}
\cortext[cor]{Corresponding author}
\address{Department of Psychological and Brain Sciences\\Dartmouth College, Hanover, NH 03755}

\begin{abstract}
  Reproducibility is a core requirement of modern scientific research.
  For computational research, reproducibility means that code should
  produce the same results, even when run on different systems.  A
  standard approach to ensuring reproducibility entails packaging a
  project's dependencies along with its primary code base.  Existing
  solutions vary in how deeply these dependencies are specified,
  ranging from virtual environments, to containers, to virtual
  machines.  Each of these existing solutions requires installing or
  setting up a system for running the desired code, increasing the
  complexity and time cost of sharing or engaging with reproducible
  science. Here, we propose a lighter-weight solution: the
  Davos package.  When used in combination with a
  notebook-based Python project, Davos provides a mechanism
  for specifying (and automatically installing) the correct versions
  of the project's dependencies.  The Davos package further
  ensures that those packages and specific versions are used every
  time the notebook's code is executed.  This enables researchers to
  share a complete reproducible copy of their code within a single
  Jupyter notebook file.
\end{abstract}

@@

\item \texttt{.project}: This attribute is a string that specifies the name of
the ``project'' associated with the current notebook. As described in
Section~\ref{subsec:projects}, a notebook's project determines where and how
any \textttt{smuggle}d dependencies are installed if they are not available in
the current runtime environment. By default, this attribute is named according
to the current notebook's absolute file path. However, the project name may be
customized to enable shared dependency installations across notebooks (see
Sec.~\ref{subsec:projects}).

@@

As of this writing, Davos can install packages using \textt{pip}, but
not other standard Python package management systems such as \texttt{conda}.
Therefore packages that are not installable via \texttt{pip} are currently
unsupported by Davos.  We anticipate adding support for other
package management systems, including \texttt{conda} in a future release.

>>>>

\title{Davos: a Python package ``smuggler'' for constructing
  lightweight reproducible notebooks}
\author{Paxton C. Fitzpatrick}
\author{Jeremy R. Manning\textsuperscript{\textsubscript{\scriptsize *}}}
\ead{Jeremy.R.Manning@Dartmouth.edu}
\cortext[cor]{Corresponding author}
\address{Department of Psychological and Brain Sciences\\Dartmouth College, Hanover, NH 03755}

\begin{abstract}
  Reproducibility is a core requirement of modern scientific research.
  For computational research, reproducibility means that code should
  produce the same results, even when run on different systems.  A
  standard approach to ensuring reproducibility entails packaging a
  project's dependencies along with its primary code base.  Existing
  solutions vary in how deeply these dependencies are specified,
  ranging from virtual environments, to containers, to virtual
  machines.  Each of these existing solutions requires installing or
  setting up a system for running the desired code, increasing the
  complexity and time cost of sharing or engaging with reproducible
  science. Here, we propose a lighter-weight solution: the
  Davos package.  When used in combination with a
  notebook-based Python project, Davos provides a mechanism
  for specifying the correct versions of the project's 
  dependencies directly within the code that requires them, 
  and automatically installing them in an isolated environment 
  when the code is run. The Davos package further
  ensures that those packages and specific versions are used every
  time the notebook's code is executed.  This enables researchers to
  share a complete reproducible copy of their code within a single
  Jupyter notebook file.
\end{abstract}

@@

\item \texttt{.project}: This attribute is a string that specifies the name of
the ``project'' associated with the current notebook. As described in
Section~\ref{subsec:projects}, a notebook's project determines where and how
any \texttt{smuggle}d dependencies are installed if they are not available in
the current runtime environment. By default, this attribute is named according
to the current notebook's absolute file path. However, the project name may be
customized to enable shared dependency installations across notebooks (see
Sec.~\ref{subsec:projects}).

@@

As of this writing, Davos can install packages using \texttt{pip}, but
not other standard Python package management systems such as \texttt{conda}.
Therefore packages that are not installable via \texttt{pip} are currently
unsupported by Davos.  We anticipate adding support for other
package management systems, including \texttt{conda} in a future release.
